---
title: "Mindset-Mindfulness Experiment Data Analysis"
author: "Tamas Nagy"
date: "10/9/2020"
output: 
  html_document:
   theme: spacelab
   code_download: true
   toc: true
   toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(sjPlot)
library(pscl)
library(performance)
library(ggbeeswarm)
library(skimr)

theme_set(theme_light())
```

# Read data

Data processing is available in "script/data\_processing.R". We only use the processed data.

```{r read data, message=FALSE, warning=FALSE}
processed_final <- read_csv("data/processed_final.csv")

```

# Data exploration and descriptives

## Sample

TODO

## Main variables

First, we present the main descriptives of the whole sample for the outcomes and potential moderators.

```{r}
processed_final %>% 
  select(extra_tasks, ms_mean, cams_mean, risc_mean, grit_mean, sc_mean, se_mean, iq_final:iq_warmup, out_1:out_3) %>% 
  skim()
```

Second, we present the outcomes and potential moderators grouped by the manipulated variables (mindset and intervention).

```{r}
processed_final %>% 
  select(mindset, intervention, extra_tasks, ms_mean, cams_mean, risc_mean, grit_mean, sc_mean, se_mean, iq_final:iq_warmup, out_1:out_3) %>% 
  group_by(mindset, intervention) %>% 
  skim()
```

The main outcome variable is the number of extra tasks that were performed in the optional practice block.

```{r}
processed_final %>% 
  ggplot() +
  aes(x = extra_tasks) +
  geom_histogram(bins = 20) +
  labs(title = "Distribution of the # of extra tasks")
```

The secondary outcomes are the IQ test points obtained at three different points.

```{r}
processed_final %>% 
  select(iq_warmup, iq_real, iq_final) %>% 
  pivot_longer(everything()) %>% 
  mutate(name = fct_inorder(name)) %>% 
  ggplot() +
  aes(x = value) +
  geom_histogram(bins = 25) +
  scale_x_continuous(labels = scales::percent_format()) +
  facet_wrap(~name)
```

# Manipulation check

The manipulation for mindset was successful, as those in the fixed mindset group had a stronger belief that intelligence cannot be changed over time.

```{r Mindest manipulation check}

processed_final %>% 
  lm(mc_3 ~ mindset, data = .) %>% 
  summary()

processed_final %>% 
  ggplot() +
  aes(x = mindset, y = mc_3, fill = mindset) +
  geom_boxplot() +
  scale_fill_viridis_d() +
  labs(title = "Statement: \"Your intelligence is an attribute that you cannot change over time\"",
       y = "Likert scale (1-6)")
```

```{r Mindfulness manipulation check}

processed_final %>% 
  lm(mc_1 ~ intervention, data = .) %>% 
  summary()

processed_final %>% 
  ggplot() +
  aes(x = intervention, y = mc_1, fill = intervention) +
  geom_boxplot() +
  scale_fill_viridis_d() +
  labs(title = "Question: \"How much could you get into a calm and focused state of mind?\"",
       y = "Likert scale (1-6)")

```

Those with higher dispositional growth mindset and / or mindullness were

```{r}
processed_final %>% 
  select(mc_1, mc_3, cams_mean, ms_mean) %>%
  ggplot() +
  aes(y = mc_3, x = ms_mean) +
  geom_point(alpha = .1) +
  geom_smooth(method = lm) +
  labs(x = "Dispositional growth mindset", y = "Statement: \"Your intelligence is an attribute that you cannot change over time\"")

```

```{r}
processed_final %>% 
  select(mc_1, mc_3, cams_mean, ms_mean) %>%
  ggplot() +
  aes(y = mc_1, x = cams_mean) +
  geom_point(alpha = .1) +
  geom_smooth(method = lm) +
  labs(x = "Dispositional mindfulness", y = "Question: \"How much could you get into a calm and focused state of mind?\"")
```

# Test Main hypothesis

We test the main hypothesis, that is the association of the mindset (fixed vs. growth) and intervention (mindfulness vs. control)

```{r test main hypothesis}
mod_1 <- glm(extra_tasks ~ mindset * intervention, 
           family = "poisson", 
           data = processed_final)

mod_2 <- glm(extra_tasks ~ mindset + intervention, 
             family = "poisson",
             data = processed_final)

tab_model(mod_1, mod_2, 
          dv.labels = c("Interaction", "Only main effects"),
          show.aic = TRUE, 
          show.stat = TRUE, 
          p.style = "numeric", 
          show.loglik = TRUE, 
          show.dev = TRUE, 
          show.zeroinf = TRUE)

# The model with the interaction term doesn't have a added value.
AIC(mod_1, mod_2)
BIC(mod_1, mod_2)

# We should check for overdispersion and zero-inflation
check_overdispersion(mod_1)
check_zeroinflation(mod_1)

```

Although we found a significant effect of mindset in the expected direction -- i.e. growth mindset increases the motivation to solve more practice tasks -- we found that the assumptions for poisson regression are not met. The tests show both overdispersion and zero-inflation, therefore we need to use a model that corrects for these.

```{r}
# Negative binomial model
mod_3 <- MASS::glm.nb(extra_tasks ~ mindset * intervention,
                      data = processed_final)

# Zero inflated poisson model
mod_4 <- zeroinfl(extra_tasks ~ mindset * intervention, dist = "poisson",
         data = processed_final) 

# Zero inflated negative binomial model (should be used)
mod_5 <- zeroinfl(extra_tasks ~ mindset * intervention, dist = "negbin",
                  data = processed_final)

tab_model(mod_3, mod_4, mod_5, 
          dv.labels = c("Negative binomial", "Zero-inflated poisson", "Zero-inflated negative binomial"),
          show.aic = TRUE, 
          show.stat = TRUE, 
          p.style = "numeric", 
          show.loglik = TRUE,
          show.dev = TRUE, 
          show.fstat = TRUE,
          show.zeroinf = TRUE)
```

The model that accounts for both overdispersion and zero-inflation does not show a significant effect neither for mindset, nor for the mindfulness.
