---
title: "Mindset-Mindfulness Experiment Data Analysis"
author: "XXX"
date: "21/7/2021"
output: 
  html_document:
   theme: spacelab
   code_download: true
   toc: true
   toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(broom)
library(sjPlot)
library(pscl)
library(performance)
library(skimr)
library(report)
library(ggbeeswarm)
library(scales)
library(gt)

theme_set(theme_light())
```

# Read data

Data processing is available in "script/data\_processing.R". We only use the processed data.

```{r read data, message=FALSE, warning=FALSE}
processed_final <- read_csv(here::here("data/processed_final.csv"))

```

# Data exploration and descriptives

## Sample

```{r results = "asis"}
processed_final %>% 
  report_participants(sex = "gender")
```

```{r}
processed_final %>% 
  select(gender, education, field, meditation, coffee, alcohol) %>% 
  mutate(across(where(is.character), as.factor)) %>% 
  summary()
```

## Descriptive statistics {.tabset}

### All participants

First, we present the main descriptives of the whole sample for the outcomes and potential moderators.

```{r}
processed_final %>%
  select(
    extra_tasks,
    ms_mean,
    cams_mean,
    risc_mean,
    grit_mean,
    sc_mean,
    se_mean,
    iq_final:iq_warmup,
    out_1:out_3) %>%
  skim()
```

### Grouped by manipulated variables

Second, we present the outcomes and potential moderators grouped by the manipulated variables (mindset and mindfulness induction).

```{r}
processed_final %>%
  select(
    mindset,
    intervention,
    extra_tasks,
    ms_mean,
    cams_mean,
    risc_mean,
    grit_mean,
    sc_mean,
    se_mean,
    iq_final:iq_warmup,
    out_1:out_3) %>%
  group_by(mindset, intervention) %>%
  skim()
```

## Compare baseline characteristics

```{r}
# Group Ns
processed_final %>% 
  count(mindset, intervention) %>% 
  pivot_wider(names_from = c(mindset, intervention),
              names_sep = " - ",
              values_from = n) %>% 
  gt() %>% 
    tab_options(row.striping.include_table_body = TRUE,
              row.striping.background_color = "#EEEEEE", 
              row.striping.include_stub = TRUE,
              column_labels.background.color = "#CCCCCC",
              column_labels.font.weight = "bold") %>% 
   tab_header(title = "Number of participants by group")

# Group gender Ns
processed_final %>% 
  count(mindset, intervention, Gender = gender) %>% 
    pivot_wider(names_from = c(mindset, intervention),
              names_sep = " - ",
              values_from = n) %>% 
  gt() %>% 
    tab_options(row.striping.include_table_body = TRUE,
              row.striping.background_color = "#EEEEEE", 
              row.striping.include_stub = TRUE,
              column_labels.background.color = "#CCCCCC",
              column_labels.font.weight = "bold") %>% 
   tab_header(title = "Number of participants of each gender by group")
```


```{r}
scale_names <- c("age" = "Age",
                 "gender" = "Gender: Male",
                 "ms" = "Prior growth mindset",
                 "cams" = "Trait mindfulness",
                 "risc" = "Ego-resilience",
                 "grit" = "Grit",
                 "sc" = "Self-compassion",
                 "se" = "Global self-esteem")

processed_final %>%
  select(
    mindset, intervention,
    gender, age, 
    ms_mean, cams_mean, risc_mean, grit_mean, sc_mean, se_mean) %>%
  mutate(gender = recode(gender, `Female` = 0L, `Male` = 1L)) %>% 
  group_by(mindset, intervention) %>%
  summarise(across(gender:se_mean, 
                   list("Mean" = mean, "SD" = sd), na.rm = TRUE), 
            .groups = "drop") %>% 
  pivot_longer(-c("mindset", "intervention")) %>% 
  mutate(name = str_remove(name, "_mean")) %>% 
  separate(name, into = c("Measure", "stat")) %>% 
  pivot_wider(names_from = "stat", values_from = "value") %>% 
  mutate(Measure = recode(Measure, !!!scale_names)) %>% 
  unite("group", c("mindset", "intervention"), sep = "-") %>% 
  mutate(across(c(Mean, SD), ~round(.x, 2) %>% 
                              format(nsmall = 2))) %>% 
  unite("mn", c("Mean", "SD"), sep = " (") %>% 
  mutate(mn = paste0(mn, ")")) %>% 
  pivot_wider(names_from = "group", values_from = "mn") %>% 
  mutate(across(-Measure, ~if_else(Measure == "Gender: Male", 
                                    str_remove(.x, "\\(.*\\)") %>% 
                                       parse_number() %>% 
                                       percent(accuracy = .1),
                                    .x) %>% 
                           str_squish())) %>% 
  gt() %>% 
  tab_spanner(label = "Group",
              columns = `Fixed-Control`:`Growth-Mindfulness`) %>% 
  tab_options(row.striping.include_table_body = TRUE,
              row.striping.background_color = "#EEEEEE", 
              row.striping.include_stub = TRUE,
              column_labels.background.color = "#CCCCCC",
              column_labels.font.weight = "bold" 
              )
  
```

None of the groups differed in any trait characteristics. The following table shows the 

```{r}
processed_final %>%
  select(
    mindset,
    intervention,
    gender, age,
    ms_mean,
    cams_mean,
    risc_mean,
    grit_mean,
    sc_mean,
    se_mean) %>%
  mutate(gender = recode(gender, `Female` = 0L, `Male` = 1L)) %>% 
  pivot_longer(-c(mindset, intervention)) %>% 
  mutate(name = str_remove(name, "_mean") %>% 
                recode(!!!scale_names)) %>% 
  group_by(name) %>% 
  nest() %>% 
  mutate(mod = map(data, ~lm(value ~  mindset * intervention, data = .x) %>% 
                          tidy())) %>% 
  unnest(mod) %>% 
  select(-data) %>% 
  gt() %>% 
  fmt_number(estimate:statistic, decimals = 2) %>% 
  fmt_number(p.value, decimals = 4) %>% 
  tab_options(row.striping.include_table_body = TRUE,
              row.striping.background_color = "#EEEEEE", 
              row.striping.include_stub = TRUE,
              column_labels.background.color = "#CCCCCC",
              column_labels.font.weight = "bold", 
              row_group.background.color = "#CCCCCC", 
              row_group.font.weight = "bold") 
  
```

The main outcome variable is the number of extra tasks that were performed in the optional practice block.

```{r}
processed_final %>% 
  ggplot() +
  aes(x = extra_tasks) +
  geom_histogram(bins = 20) +
  labs(title = "Distribution of the # of extra tasks")
```

The secondary outcomes are the IQ test points obtained at three different points.

```{r}
processed_final %>% 
  select(iq_warmup, iq_real, iq_final) %>% 
  pivot_longer(everything()) %>% 
  mutate(name = fct_inorder(name)) %>% 
  ggplot() +
  aes(x = value) +
  geom_histogram(bins = 25) +
  scale_x_continuous(labels = percent_format()) +
  facet_wrap(~name)
```

# Induction check

The induction for mindset was successful, as those in the fixed mindset group had a stronger belief that intelligence cannot be changed over time. On the other hand, the mindfulness induction did not make the participants more mindful.

## Mindset manipulation check

```{r Mindest manipulation check}

mindset_stat <- lm(mc_3 ~ mindset + ms_mean, data = processed_final)

tab_model(mindset_stat, show.df = TRUE)

effectsize::cohens_d(mc_3 ~ mindset, data = processed_final)

mindset_check <-
  processed_final %>% 
  ggplot() +
  aes(y = mindset, x = mc_3, fill = mindset) +
  geom_boxplot(show.legend = FALSE, width = .5, alpha = .7, outlier.alpha = 0) +
  geom_jitter(width = .2, alpha = .5, height = .2, show.legend = FALSE) +
  labs(subtitle = "Answer: \"Your intelligence is an attribute that you cannot change over time (1-6)\"",
       y = NULL,
       x = NULL)
```

## Mindfulness induction manipulation check

```{r Mindfulness manipulation check}

mindfulness_stat <- lm(mc_1 ~ intervention + cams_mean, data = processed_final)

tab_model(mindfulness_stat, show.df = TRUE)
  
effectsize::cohens_d(mc_1 ~ intervention, data = processed_final)

mindfulness_check <- 
  processed_final %>% 
  ggplot() +
  aes(y = intervention, x = mc_1, fill = intervention) +
  geom_boxplot(show.legend = FALSE, width = .5, alpha = .7, outlier.alpha = 0) +
  geom_jitter(width = .2, alpha = .5, height = .2, show.legend = FALSE) +
  scale_fill_viridis_d() +
  labs(subtitle = "Answer: \"How much could you get into a calm and focused state of mind? (1-6)\"",
       x = NULL,
       y = NULL)

mindset_check + mindfulness_check + patchwork::plot_layout(nrow = 2) 

# ggsave("docs/figure_3.png", dpi = 300)

```

# Dispositional confounders of the manipulation {.tabset}

## Dispositional mindset

Those with higher dispositional growth mindset and / or mindfulness were less likely to believe that intelligence cannot be changed over time.

```{r}
processed_final %>% 
  select(mc_1, mc_3, cams_mean, ms_mean) %>%
  ggplot() +
  aes(y = mc_3, x = ms_mean) +
  geom_point(alpha = .1) +
  geom_smooth(method = lm) +
  labs(x = "Dispositional growth mindset", 
       y = "Statement: \"Your intelligence is an attribute that you cannot change over time\"")

```

## Dispositional mindfulness

Similarly, those with dispositional mindfulness were more likely to be able to get into a calm and focused state.

```{r}
processed_final %>% 
  select(mc_1, mc_3, cams_mean, ms_mean) %>%
  ggplot() +
  aes(y = mc_1, x = cams_mean) +
  geom_point(alpha = .1) +
  geom_smooth(method = lm) +
  labs(x = "Dispositional mindfulness", y = "Question: \"How much could you get into a calm and focused state of mind?\"")
```

# Test main outcomes

## Number of solved optional exercises

We test the main hypothesis, that is the association of the mindset (fixed vs. growth) and mindfulness induction (mindfulness vs. control) with the number of solved optional exercises.

```{r test main hypothesis}
mod_1 <- glm(extra_tasks ~ mindset * intervention, 
           family = "poisson", 
           data = processed_final)

mod_2 <- glm(extra_tasks ~ mindset + intervention, 
             family = "poisson",
             data = processed_final)

tab_model(mod_1, mod_2, 
          dv.labels = c("Interaction", "Only main effects"),
          show.aic = TRUE, 
          show.stat = TRUE, 
          p.style = "numeric", 
          show.loglik = TRUE, 
          show.dev = TRUE, 
          show.zeroinf = TRUE)

# The model with the interaction term doesn't have a added value.
AIC(mod_1, mod_2)
BIC(mod_1, mod_2)

# We should check for overdispersion and zero-inflation
check_overdispersion(mod_1)
check_zeroinflation(mod_1)

```

Although we found a significant effect of mindset in the expected direction -- i.e. growth mindset increases the motivation to solve more practice tasks -- we found that the assumptions for poisson regression are not met. The tests show both overdispersion and zero-inflation, therefore we need to use a model that corrects for these.

```{r cache = TRUE}
# Negative binomial model
mod_3 <- MASS::glm.nb(extra_tasks ~ mindset * intervention,
                      data = processed_final)

# Zero inflated poisson model
mod_4 <- zeroinfl(extra_tasks ~ mindset * intervention, dist = "poisson",
         data = processed_final) 

# Zero inflated negative binomial model (should be used)
mod_5 <- zeroinfl(extra_tasks ~ mindset * intervention, dist = "negbin",
                  data = processed_final)


# Null model for model comparisons
mod_0 <- zeroinfl(extra_tasks ~ 1, data = processed_final, dist = "negbin")

tab_model(
          mod_5, 
          # bootstrap = TRUE,
          dv.labels = c("Zero-inflated negative binomial"),
          show.aic = TRUE, 
          show.stat = TRUE, 
          p.style = "numeric", 
          show.loglik = TRUE,
          show.dev = TRUE, 
          show.fstat = TRUE,
          show.zeroinf = TRUE 
          # file = here::here("docs/zinb.html")
          )
  
```

```{r include = FALSE, eval = FALSE}
summary(mod_5)
BIC(mod_5)
```

The model that accounts for both overdispersion and zero-inflation does not show a significant effect neither for mindset, nor the mindfulness.

```{r results = "asis"}
report(mod_5) %>% 
  summary()

```

### Bayes Factors

We calculated the Bayes Factors for models with different predictor terms. Based on the low BFs, it is very unlikely that any of the inductions would have an effect on the outcome.

```{r}
# BF for full model with interaction term
exp((BIC(mod_0) - BIC(mod_5))/2)

# BF mindset
mod_5ms <- zeroinfl(extra_tasks ~ mindset, dist = "negbin",
                  data = processed_final)

exp((BIC(mod_0) - BIC(mod_5ms))/2)

# BF mindfulness
mod_5mf <- zeroinfl(extra_tasks ~ intervention, dist = "negbin",
                  data = processed_final)

exp((BIC(mod_0) - BIC(mod_5mf))/2)
```

Bayes Factor for for the zero inflated negative binomial model: `format(exp((BIC(mod_0) - BIC(mod_5))/2), digits = 4)` 
This means, it is very unlikely that the model that contains both the mindset and mindfulness interventions (and their interaction) to have an associations with the number of completed optional exercises.

## Proportion of correct answers in the "real" IQ test

```{r}
iq_mod <- lm(iq_real ~ mindset * intervention, 
             data = processed_final)

tab_model(iq_mod)
report(iq_mod) %>% 
  summary()

tab_model(iq_mod, 
          dv.labels = "\"Real\" IQ test result",
          show.stat = TRUE, 
          show.est = FALSE,
          show.std = TRUE,
          show.aic = TRUE,
          show.fstat = TRUE, 
          robust = TRUE
          # file = here::here("docs/realiq.html")
          )

check_model(iq_mod, 
            check = c("vif", "qq", "normality", "ncv", "homogeneity", "reqq"))

```

```{r include = FALSE, eval=FALSE}

summary(iq_mod)
BIC(iq_mod)
```


```{r results = "asis"}
report(iq_mod) %>% 
  summary()
```

# Secondary outcomes

## Task enjoyment/boredom

```{r}
bored_mod <- lm(out_2 ~ mindset * intervention, 
                data = processed_final)

tab_model(bored_mod, 
          dv.labels = "Boredom",
          show.stat = TRUE, 
          show.est = FALSE,
          show.std = TRUE, 
          show.fstat = TRUE,
          file = here::here("docs/boredom.html")
          )

check_model(bored_mod, 
            check = c("vif", "qq", "normality", "ncv", "homogeneity", "reqq"))
```

```{r results = "asis"}
report(bored_mod) %>% 
  summary()
```

## Anxiety/stress

```{r}
stress_mod <- lm(out_1 ~ mindset * intervention, 
                 data = processed_final)

tab_model(stress_mod, 
          # bootstrap = TRUE,
          dv.labels = "Stress/anxiety",
          show.stat = TRUE, 
          show.est = FALSE,
          show.std = TRUE, 
          show.fstat = TRUE,
        file = here::here("docs/anxiety.html")
        )

check_model(stress_mod, 
            check = c("vif", "qq", "normality", "ncv", "homogeneity", "reqq"))
```

```{r, eval=FALSE, include=FALSE}
tab_model(stress_mod, bored_mod,
          # bootstrap = TRUE,
          dv.labels = c("Stress/anxiety", "Boredom"),
          show.stat = TRUE, 
          show.est = FALSE,
          show.std = TRUE, 
          show.fstat = TRUE,
          robust = TRUE,
          show.aic = TRUE
          # file = here::here("docs/anxiety-boredom.html")
        )

summary(stress_mod)
summary(bored_mod)

BIC(stress_mod)
BIC(bored_mod)
```


```{r results = "asis"}
report(stress_mod) %>% 
  summary()
```

## Achievement goals

None of the achievement goal variables were associated with the manipulated variables.

```{r}

ag_mod <-
  processed_final %>% 
  select(response_id, agq_sap:agt_p_tav, mindset, intervention, extra_tasks) %>% 
  pivot_longer(agq_sap:agt_p_tav) %>% 
  mutate(value = if_else(str_detect(name, "_p_") & extra_tasks == 0, 
                         NA_real_,
                         value)) %>% 
  drop_na(value) %>% 
  group_nest(name) %>% 
  mutate(model = map(data, 
                     ~lm(value ~ mindset * intervention, 
                         data = .x)))

pull(ag_mod, model) %>% 
  set_names(ag_mod$name) %>% 
  tab_model(., 
            dv.labels = ag_mod$name,
            show.stat = TRUE, 
            show.est = FALSE,
            show.std = TRUE, 
            show.fstat = TRUE)
  
```

# Moderator effects

The primary outcomes are checked for moderator effects (the upper row means the name of the moderator, that is used in the table as "value").

## Number of solved optional exercises

```{r}
moderators_m1 <- 
  processed_final %>%
  select(response_id, extra_tasks, mindset, intervention, 
         age, gender, education,
         ms_mean:grit_mean) %>% 
  # Scale all continuous predictors
  mutate(across(ms_mean:grit_mean, scale)) %>% 
  pivot_longer(cols = c(age, ms_mean:grit_mean)) %>% 
  group_nest(name) %>% 
  mutate(model = map(data, 
                     ~zeroinfl(extra_tasks ~ mindset * intervention * value, 
                      dist = "negbin",
                      data = .x)))


pull(moderators_m1, model) %>% 
  set_names(moderators_m1$name) %>% 
  tab_model(., 
            dv.labels = moderators_m1$name,
            show.aic = TRUE, 
            show.stat = TRUE, 
            p.style = "numeric", 
            show.loglik = TRUE, 
            show.dev = TRUE, 
            show.zeroinf = TRUE,
            file = here::here("docs/moderators.html")
          )


```

Those who had a higher dispositional mindfulness or had higher self-esteem, and received the mindfulness induction solved approximately 1.5 times more optional tasks, compared to those who were in the fixed mindset and control conditions.

```{r}

tab_model(moderators_m1$model[c(2, 7)],
          dv.labels = c("Dispositional mindfulness",
                        "Self-esteem"),
          # bootstrap = TRUE,
          show.aic = TRUE, 
          show.stat = TRUE, 
          p.style = "numeric", 
          show.loglik = TRUE, 
          show.dev = TRUE, 
          # file = here::here("docs/moderators.html"),
          show.zeroinf = TRUE)

BIC(moderators_m1$model[[2]])
BIC(moderators_m1$model[[4]])

# BF for full model with interaction term
exp((BIC(mod_0) - BIC(moderators_m1$model[[2]]))/2)

tab_model(
          mod_5, 
          moderators_m1$model[[2]],
          # bootstrap = TRUE,
          dv.labels = c("Simple model",
                        "Moderator model"),
          show.aic = TRUE, 
          show.stat = TRUE, 
          p.style = "numeric", 
          show.loglik = TRUE,
          show.dev = TRUE, 
          show.fstat = TRUE,
          show.zeroinf = TRUE 
          # file = here::here("docs/zinb-mod.html")
          )

```

### Visualize moderator effect

```{r}
cams_mod <- 
  zeroinfl(extra_tasks ~ intervention * scale(cams_mean),
           dist = "negbin",
           data = processed_final) 

mod_plot <-
  processed_final %>% 
  mutate(.fitted = predict(cams_mod, type = "response")) %>% 
  ggplot() +
  aes(x = cams_mean, y = extra_tasks, color = intervention) +
  geom_point(alpha = .3, size = 2) +
  geom_line(aes(y = .fitted), alpha = .6, size = 1.2) +
  scale_color_viridis_d() +
  labs(color = "Group",
       y = "Solved optional tasks",
       x = "Dispositional mindfulness")

mod_plot 

# ggsave(plot = mod_plot, filename = "docs/figure_4.png", dpi = 300)
```

## Number of correct answers in the "real" IQ test

Here we only found that the score on the "real" IQ test was weakly associated with the grit score (the upper row means the name of the moderator, that is used in the table as "value").

```{r}
moderators_m2 <-
  processed_final %>%
  select(response_id, mindset, intervention, 
         iq_real,
         age, ms_mean:grit_mean) %>% 
  # Scale all continuous predictors
  mutate(across(c(iq_real, ms_mean:grit_mean), scale)) %>% 
  pivot_longer(cols = c(age, ms_mean:grit_mean)) %>% 
  group_nest(name) %>% 
  mutate(model = map(data, 
                     ~lm(iq_real ~ mindset * intervention * value, 
                      data = .x)))


pull(moderators_m2, model) %>% 
  set_names(moderators_m2$name) %>% 
  tab_model(., 
            dv.labels = moderators_m2$name,
            show.stat = TRUE,
            show.est = FALSE,
            show.std = TRUE, 
            show.fstat = TRUE)
```

