---
title: "Mindset-Mindfulness Experiment Data Analysis"
author: "Tamas Nagy"
date: "10/9/2020"
output: 
  html_document:
   theme: spacelab
   code_download: true
   toc: true
   toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(sjPlot)
library(pscl)
library(performance)
library(ggbeeswarm)
library(skimr)
library(report)

theme_set(theme_light())
```

# Read data

Data processing is available in "script/data\_processing.R". We only use the processed data.

```{r read data, message=FALSE, warning=FALSE}
processed_final <- read_csv(here::here("data/processed_final.csv"))

```

# Data exploration and descriptives

## Sample

```{r results = "asis"}
processed_final %>% 
  report_participants(sex = "gender")
```

```{r}
processed_final %>% 
  select(age, term_no) %>% 
  skim()

processed_final %>% 
  select(gender, education, field, meditation, coffee, alcohol) %>% 
  mutate(across(where(is.character), as.factor)) %>% 
  summary()
```

## Main variables

First, we present the main descriptives of the whole sample for the outcomes and potential moderators\_m1.

```{r}
processed_final %>% 
  select(extra_tasks, ms_mean, cams_mean, risc_mean, grit_mean, sc_mean, se_mean, iq_final:iq_warmup, out_1:out_3) %>% 
  skim()
```

Second, we present the outcomes and potential moderators\_m1 grouped by the manipulated variables (mindset and intervention).

```{r}
processed_final %>% 
  select(mindset, intervention, extra_tasks, ms_mean, cams_mean, risc_mean, grit_mean, sc_mean, se_mean, iq_final:iq_warmup, out_1:out_3) %>% 
  group_by(mindset, intervention) %>% 
  skim()
```

The main outcome variable is the number of extra tasks that were performed in the optional practice block.

```{r}
processed_final %>% 
  ggplot() +
  aes(x = extra_tasks) +
  geom_histogram(bins = 20) +
  labs(title = "Distribution of the # of extra tasks")
```

The secondary outcomes are the IQ test points obtained at three different points.

```{r}
processed_final %>% 
  select(iq_warmup, iq_real, iq_final) %>% 
  pivot_longer(everything()) %>% 
  mutate(name = fct_inorder(name)) %>% 
  ggplot() +
  aes(x = value) +
  geom_histogram(bins = 25) +
  scale_x_continuous(labels = scales::percent_format()) +
  facet_wrap(~name)
```

# Manipulation check

The manipulation for mindset was successful, as those in the fixed mindset group had a stronger belief that intelligence cannot be changed over time.

```{r Mindest manipulation check}

processed_final %>% 
  lm(mc_3 ~ mindset, data = .) %>% 
  summary()

processed_final %>% 
  ggplot() +
  aes(x = mindset, y = mc_3, fill = mindset) +
  geom_boxplot() +
  scale_fill_viridis_d() +
  labs(title = "Statement: \"Your intelligence is an attribute that you cannot change over time\"",
       y = "Likert scale (1-6)")
```

```{r Mindfulness manipulation check}

processed_final %>% 
  lm(mc_1 ~ intervention, data = .) %>% 
  summary()

processed_final %>% 
  ggplot() +
  aes(x = intervention, y = mc_1, fill = intervention) +
  geom_boxplot() +
  scale_fill_viridis_d() +
  labs(title = "Question: \"How much could you get into a calm and focused state of mind?\"",
       y = "Likert scale (1-6)")

```

Those with higher dispositional growth mindset and / or mindullness were less likely to believe that intelligence cannot be changed over time.

```{r}
processed_final %>% 
  select(mc_1, mc_3, cams_mean, ms_mean) %>%
  ggplot() +
  aes(y = mc_3, x = ms_mean) +
  geom_point(alpha = .1) +
  geom_smooth(method = lm) +
  labs(x = "Dispositional growth mindset", y = "Statement: \"Your intelligence is an attribute that you cannot change over time\"")

```

Similarly, those with dispositional mindfulness were more likely to be able to get into a calm and focused state.

```{r}
processed_final %>% 
  select(mc_1, mc_3, cams_mean, ms_mean) %>%
  ggplot() +
  aes(y = mc_1, x = cams_mean) +
  geom_point(alpha = .1) +
  geom_smooth(method = lm) +
  labs(x = "Dispositional mindfulness", y = "Question: \"How much could you get into a calm and focused state of mind?\"")
```

# Test main outcomes

## Number of solved optional exercises

We test the main hypothesis, that is the association of the mindset (fixed vs. growth) and intervention (mindfulness vs. control) with the number of solved optional exercises.

```{r test main hypothesis}
mod_1 <- glm(extra_tasks ~ mindset * intervention, 
           family = "poisson", 
           data = processed_final)

mod_2 <- glm(extra_tasks ~ mindset + intervention, 
             family = "poisson",
             data = processed_final)

tab_model(mod_1, mod_2, 
          dv.labels = c("Interaction", "Only main effects"),
          show.aic = TRUE, 
          show.stat = TRUE, 
          p.style = "numeric", 
          show.loglik = TRUE, 
          show.dev = TRUE, 
          show.zeroinf = TRUE)

# The model with the interaction term doesn't have a added value.
AIC(mod_1, mod_2)
BIC(mod_1, mod_2)

# We should check for overdispersion and zero-inflation
check_overdispersion(mod_1)
check_zeroinflation(mod_1)

```

Although we found a significant effect of mindset in the expected direction -- i.e. growth mindset increases the motivation to solve more practice tasks -- we found that the assumptions for poisson regression are not met. The tests show both overdispersion and zero-inflation, therefore we need to use a model that corrects for these.

```{r cache = TRUE}
# Negative binomial model
mod_3 <- MASS::glm.nb(extra_tasks ~ mindset * intervention,
                      data = processed_final)

# Zero inflated poisson model
mod_4 <- zeroinfl(extra_tasks ~ mindset * intervention, dist = "poisson",
         data = processed_final) 

# Zero inflated negative binomial model (should be used)
mod_5 <- zeroinfl(extra_tasks ~ mindset * intervention, dist = "negbin",
                  data = processed_final)

tab_model(mod_3, mod_4, mod_5, 
          bootstrap = TRUE,
          dv.labels = c("Negative binomial", "Zero-inflated poisson", "Zero-inflated negative binomial"),
          show.aic = TRUE, 
          show.stat = TRUE, 
          p.style = "numeric", 
          show.loglik = TRUE,
          show.dev = TRUE, 
          show.fstat = TRUE,
          show.zeroinf = TRUE)
```

The model that accounts for both overdispersion and zero-inflation does not show a significant effect neither for mindset, nor for the mindfulness.

```{r results = "asis"}
report(mod_5) %>% 
  summary()

```

## Number of correct answers in the "real" IQ test

```{r}
iq_mod <- lm(iq_real ~ mindset * intervention, 
             data = processed_final)

tab_model(iq_mod, 
          dv.labels = "\"Real\" IQ test result",
          # bootstrap = TRUE,
          show.stat = TRUE, 
          show.est = FALSE,
          show.std = TRUE, 
          show.fstat = TRUE)

check_model(iq_mod, 
            check = c("vif", "qq", "normality", "ncv", "homogeneity", "reqq"))
```

```{r results = "asis"}
report(iq_mod) %>% 
  summary()
```

# Secondary outcomes

## Task enjoyment/boredom

```{r}
bored_mod <- lm(out_2 ~ mindset * intervention, 
                data = processed_final)

tab_model(bored_mod, 
          # bootstrap = TRUE,
          dv.labels = "Boredom",
          show.stat = TRUE, 
          show.est = FALSE,
          show.std = TRUE, 
          show.fstat = TRUE)

check_model(bored_mod, 
            check = c("vif", "qq", "normality", "ncv", "homogeneity", "reqq"))
```

```{r results = "asis"}
report(bored_mod) %>% 
  summary()
```

## Anxiety/stress

```{r}
stress_mod <- lm(out_1 ~ mindset * intervention, 
                 data = processed_final)

tab_model(stress_mod, 
          # bootstrap = TRUE,
          dv.labels = "Stress/anxiety",
          show.stat = TRUE, 
          show.est = FALSE,
          show.std = TRUE, 
          show.fstat = TRUE)

check_model(stress_mod, 
            check = c("vif", "qq", "normality", "ncv", "homogeneity", "reqq"))
```

```{r results = "asis"}
report(stress_mod) %>% 
  summary()
```

## Achievement goals

None of the achievement goal variables were associated with the manipulated variables.

```{r}

ag_mod <-
  processed_final %>% 
  select(response_id, agq_sap:agt_p_tav, mindset, intervention) %>% 
  pivot_longer(agq_sap:agt_p_tav) %>% 
  group_nest(name) %>% 
  mutate(model = map(data, 
                     ~lm(value ~ mindset * intervention, 
                         data = .x)))

pull(ag_mod, model) %>% 
  set_names(ag_mod$name) %>% 
  tab_model(., 
            dv.labels = ag_mod$name,
            show.stat = TRUE, 
            show.est = FALSE,
            show.std = TRUE, 
            show.fstat = TRUE)
  
```

# Moderator effects

The primary outcomes are checked for moderator effects (the upper row means the name of the moderator, that is used in the table as "value").

## Number of solved optional exercises

```{r}
moderators_m1 <-
  processed_final %>%
  select(response_id, extra_tasks, mindset, intervention, 
         age, gender, education,
         ms_mean:grit_mean) %>% 
  # Scale all continuous predictors
  mutate(across(ms_mean:grit_mean, scale)) %>% 
  pivot_longer(cols = c(age, ms_mean:grit_mean)) %>% 
  group_nest(name) %>% 
  mutate(model = map(data, 
                     ~zeroinfl(extra_tasks ~ mindset * intervention * value, 
                      dist = "negbin",
                      data = .x)))


pull(moderators_m1, model) %>% 
  set_names(moderators_m1$name) %>% 
  tab_model(., 
            dv.labels = moderators_m1$name,
            show.aic = TRUE, 
            show.stat = TRUE, 
            p.style = "numeric", 
            show.loglik = TRUE, 
            show.dev = TRUE, 
            show.zeroinf = TRUE)


```

Those who had a higher dispositional mindfulness or had higher self-esteem, and received the mindfulness intervention solved approximately 1.5 times more optional tasks, compared to those who were in the fixed mindset and control conditions.

```{r}

tab_model(moderators_m1$model[c(2, 7)],
          dv.labels = c("Dispositional mindfulness",
                        "Self-esteem"),
          # bootstrap = TRUE,
          show.aic = TRUE, 
          show.stat = TRUE, 
          p.style = "numeric", 
          show.loglik = TRUE, 
          show.dev = TRUE, 
          show.zeroinf = TRUE)
```

## Number of correct answers in the "real" IQ test

Here we only found that the score on the "real" IQ test was weakly associated with the grit score (the upper row means the name of the moderator, that is used in the table as "value").

```{r}
moderators_m2 <-
  processed_final %>%
  select(response_id, mindset, intervention, 
         iq_real,
         age, ms_mean:grit_mean) %>% 
  # Scale all continuous predictors
  mutate(across(c(iq_real, ms_mean:grit_mean), scale)) %>% 
  pivot_longer(cols = c(age, ms_mean:grit_mean)) %>% 
  group_nest(name) %>% 
  mutate(model = map(data, 
                     ~lm(iq_real ~ mindset * intervention * value, 
                      data = .x)))


pull(moderators_m2, model) %>% 
  set_names(moderators_m2$name) %>% 
  tab_model(., 
            dv.labels = moderators_m2$name,
            show.stat = TRUE,
            show.est = FALSE,
            show.std = TRUE, 
            show.fstat = TRUE)
```
